Secure Composition of Robust and Optimising Compilers

### 2023-07-09 popl/main.tex
add citation to parametricity

Property satisfaction is defined on whole programs, i.e., programs without missing definitions.
Thus, there is only a passive attacker model that observes the execution and, e.g., retreives secrets from that.
To consider a stronger model similarily to what existing work does~\cite{abate2019jour,abate2021extacc,patrignani2021rsc}, the concept of satisfaction is extended with {\em robustness}.
Robust satisfaction considers partial programs $\progvar$, i.e., programs with free variables, which need to be defined prior to execution.
Programs with free variables can get stuck during execution.
To remedy this, {\em linking} takes two partial programs $\progvar[_{1}],\progvar[_{2}]$ and produces a whole program $\wholeprogvar$, i.e., $\link{\progvar[_{1}]}{\progvar[_{2}]}=\wholeprogvar$.
As typically done in secure compilation~\cite{abate2019jour}, \MP{others do this too, parametricity results e.g.} this paper assumes that whole programs are the result of linking partial programs referred to as {\em context} ($\ctx$) and {\em component} ($\comp$).
The context is an arbitrary program and thus has the role of an {\em attacker} that can interact with the component by means of whatever features the programming language has.
%In this work, the semantics of the programming language is expected to differentiate between the component and the context.
With this, \Thmref{def:propsat} can be extended as follows: for \bul{components $\progvar$ to robustly satisfy a property $\pi$}, take an \iul{attacker context $\contextvar$ and link it with $\progvar$}, \oul{the result of which must satisfy $\pi$}.
%\MPin{
% the behaviour of the result?
%%%%%%%    MK: def:propsat defines satisfaction in terms of programs, no need to talk about behavior here
%}

>>>>

Property satisfaction is defined on whole programs, i.e., programs without missing definitions.
Thus, there is only a passive attacker model that observes the execution and, e.g., retreives secrets from that.
To consider a stronger model similarily to what existing work does~\cite{abate2019jour,abate2021extacc,patrignani2021rsc}, the concept of satisfaction is extended with {\em robustness}.
Robust satisfaction considers partial programs $\progvar$, i.e., programs with free variables, which need to be defined prior to execution.
Programs with free variables can get stuck during execution.
To remedy this, {\em linking} takes two partial programs $\progvar[_{1}],\progvar[_{2}]$ and produces a whole program $\wholeprogvar$, i.e., $\link{\progvar[_{1}]}{\progvar[_{2}]}=\wholeprogvar$.
As typically done in not only secure compilation~\cite{abate2019jour,devriese2018parametricity}, \MP{others do this too, parametricity results e.g.} this paper assumes that whole programs are the result of linking partial programs referred to as {\em context} ($\ctx$) and {\em component} ($\comp$).
The context is an arbitrary program and thus has the role of an {\em attacker} that can interact with the component by means of whatever features the programming language has.
%In this work, the semantics of the programming language is expected to differentiate between the component and the context.
With this, \Thmref{def:propsat} can be extended as follows: for \bul{components $\progvar$ to robustly satisfy a property $\pi$}, take an \iul{attacker context $\contextvar$ and link it with $\progvar$}, \oul{the result of which must satisfy $\pi$}.
%\MPin{
% the behaviour of the result?
%%%%%%%    MK: def:propsat defines satisfaction in terms of programs, no need to talk about behavior here
%}
